---
title: "Identifying Price Informativeness"
author: "Eduardo Davila^[Yale] & Cecilia Parlatore^[NYU Stern]"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r}

library(here); library(tidyverse); library(lubridate);
path <- here::here(); print(path); setwd(path); rm(path)

load("input/data_raw/raw_compustat.RData")

```

# Merging CCM to compustat

Note that the CRSP data is monthly, while the compustat data is quarterly/annual. Variables are in millions of dollars.
We now transform the Compustat **quarterly** data. Output: *compustatq* dataframe.

- inner join, only merge compustat if permno exists in ccmlink
- remove compustat fiscal ends that do not fall within linked period
- DATADATE gives us the close of fiscal period
- Link if any part of the period is within the link date range

```{r}

fn_compustat_ccm <- function(df_input, compustat_ccmlink){
  
  df_ccm <- compustat_ccmlink %>%
  filter(linktype %in% c("LU", "LC", "LS")) %>%
  filter(linkprim %in% c("P", "C")) %>%
  inner_join(df_input, by = "gvkey") %>%
  filter(datadate >= linkdt & (datadate <= linkenddt | is.na(linkenddt))) %>% # linkenddt = NA means ongoing
  mutate(linktype = factor(linktype, levels = c("LC", "LU", "LS")),
         linkprim = factor(linkprim, levels = c("P", "C"))) %>% 
  mutate(year  = year(datadate), month = month(datadate)) %>%
  select(datadate, year, month, gvkey, permno, everything()) %>%
  arrange(datadate, permno, linktype, linkprim) %>% 
  distinct(datadate, permno, .keep_all = T) # eliminate duplicates, due to change of fiscal year -- not a problem with annual
  
  return(df_ccm)
}

df_ccm_q <- fn_compustat_ccm(compustat_fundq, compustat_ccmlink) # quarterly
df_ccm_a <- fn_compustat_ccm(compustat_funda, compustat_ccmlink) # annual

#duplicates <- df_ccm %>% group_by(datadate, permno) %>% summarize(n = n()) %>% filter(n > 1) # select duplicates  

```

- assets = at, cashflow = oancf, netincome = ni, dividends = cdvc, longtermdebt = dltt
- assets = atq, cashflow = oancfy, netincome = niq, dividends = cdvcy,  longtermdebt = dlttq

- Annual compustat: EBIT = This item is the sum of Sales - Net (SALE) minus Cost of Goods Sold (COGS) minus Selling, General & Administrative Expense (XSGA) minus Depreciation/Amortization (DP). 
- Quarterly equivalent of this item is Operating Income After Depreciation - Quarterly (OIADPQ).

```{r}

compustat_q <- df_ccm_q %>%
  filter(year < 2018) %>% 
  mutate(book = coalesce(seqq, ceqq + pstkq, atq - ltq) + # shareholders equity
           coalesce(txditcq, 0) -   # deferred assets plus investment tax credit
           coalesce(pstkq, 0),      # preferred stock
         OpProf = revtq - coalesce(cogsq, 0) - coalesce(xintq, 0) - coalesce(xsgaq,0),
         OpProf = as.numeric(ifelse(is.na(cogsq) & is.na(xintq) & is.na(xsgaq), NA, OpProf)),
         GrProf = revtq - cogsq,
         Cflow  = ibq + coalesce(txdiq, 0) + dpq,
         Inv    = (coalesce(ppegtq - lag(ppegtq), 0) + coalesce(invtq - lag(invtq), 0)) / lag(atq),
         AstChg = (atq - lag(atq)) / lag(atq) ) %>% # lags uses previously available (may be different from 1 qr)
  mutate(ebit   = oiadpq,
         ebitda = oibdpq) %>%
  select(permno, datadate, year, month, fyearq, atq, ebit, ebitda, oancfy, niq, book, rdq) %>% 
  arrange(permno, datadate)

compustat_a <- df_ccm_a %>%
  filter(year < 2018) %>%
  mutate(book = coalesce(seq, ceq + pstk, at - lt) + # shareholders equity
           coalesce(txditc, txdb + itcb, 0) -   # deferred assets plus investment tax credit
           coalesce(pstkrv, pstkl, pstk, 0),    # preferred stock
         OpProf = revt - coalesce(cogs, 0) - coalesce(xint, 0) - coalesce(xsga,0),
         OpProf = as.numeric(ifelse(is.na(cogs) & is.na(xint) & is.na(xsga), NA, OpProf)),
         GrProf = revt - cogs,
         Cflow  = ib + coalesce(txdi, 0) + dp,
         Inv    = (coalesce(ppegt - lag(ppegt), 0) + coalesce(invt - lag(invt), 0)) / lag(at),
         AstChg = (at - lag(at)) / lag(at) ) %>% # lags uses previously available (may be different from 1 yr)
  select(permno, datadate, year, month, fyear, at, ebit, ebitda, oancf, ni, book) %>% 
  arrange(permno, datadate)

save(compustat_q, compustat_a, file = "intermediate/clean_compustat.RData")

```
