---
title: "Identifying Price Informativeness"
author: "Eduardo Davila^[Yale] & Cecilia Parlatore^[NYU Stern]"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document:  default
---

```{r echo=FALSE, include=FALSE}

library(here); library(tidyverse); library(lubridate); library(slider)
path <- here::here(); print(path); setwd(path); rm(path)

load("input/data_raw/raw_fred.RData")
load("intermediate/clean_compustat.RData")
load("intermediate/clean_crsp.RData")

deflate <- TRUE
shift   <- TRUE

```

# Deflating variables

```{r deflator}

if (deflate == TRUE) {

deflator <- deflator %>% select(-date)

crsp <- crsp %>%
  left_join(deflator, by = c("year","month")) %>%
  mutate_at(vars(mcap:adjprc), ~./deflator) %>%
  select(-deflator)

compustat_q <- compustat_q %>%
  left_join(deflator, by = c("year", "month")) %>%
  mutate_at(vars(ebit:book), ~./deflator) %>%
  select(-deflator)

compustat_a <- compustat_a %>%
  left_join(deflator, by = c("year", "month")) %>%
  mutate_at(vars(ebit:book), ~./deflator) %>%
  select(-deflator)

df_fred <- df_fred %>% 
  left_join(deflator, by = c("year", "month")) %>% 
  mutate_at(vars(cons:income), ~./deflator) %>% 
  select(-deflator) %>% 
  rename(date_fred = date)

}

```

# Making FRED data quarterly and annual

Compute moving sums

```{r}

fred_q <- df_fred %>%
  mutate(cons   = slide_dbl(cons,   sum, .before = 2, .after = 0),
         income = slide_dbl(income, sum, .before = 2, .after = 0))
  
fred_a <- df_fred %>%
  mutate(cons   = slide_dbl(cons,   sum, .before = 11, .after = 0),
         income = slide_dbl(income, sum, .before = 11, .after = 0))

```

# Merging crsp and compustat

From Compustat: "DATADATE refers to the period in which the financial activity occurred". 
If we were to map the data to real dates, we should use *fyear* instead, to guarantee that there are no gaps. (see e.g. permno = 10031)

1. Contemporary: we match the date $t$ ebit with the date $t$ price.
2. Shifted *(baseline timing)*: we match the date $t$ ebit with the price one month later (quarter) or one quarter later (annual). This timing difference allows investors to observe public earnings releases check rdq variable)

Note that in the annual merge, consumption and income are still quarterly (we'll still use)

```{r}

fn_merge <- function(crsp, compustat, df_fred){

  merged <- crsp %>%
    inner_join(compustat, by = c("permno", "year", "month")) %>%
    rename(date_crsp       = date, 
            date_compustat = datadate) %>%
    mutate(booktomarket = book/mcap) %>%
    left_join(df_fred, by = c("year", "month")) %>% 
    select(permno, year, month, date_crsp, date_compustat, date_fred, datefrac, everything())
    
  return(merged)
}

if (shift == TRUE) {

  lag_merge <- 95 # 95, 35
      
  crsp_q_shifted <- crsp %>%
    mutate(year  = year(date  - lag_merge),
           month = month(date - lag_merge)) # shifts time back
  
  crsp_a_shifted <- crsp %>%
    mutate(year  = year(date  - lag_merge),
           month = month(date - lag_merge)) # shifts time back
  
  merged_q <- fn_merge(crsp_q_shifted, compustat_q, fred_q)
  merged_a <- fn_merge(crsp_a_shifted, compustat_a, fred_a)

}

if (shift == FALSE) {
  
  merged_q <- fn_merge(crsp, compustat_q, fred_q)
  merged_a <- fn_merge(crsp, compustat_a, fred_a)

}

save(merged_a, merged_q, file = "intermediate/dataset_merged.RData")

```
